\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black,
}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.2in}

\begin{document}

\noindent Ilyas Ibragimov \\
New York, NY \\
\href{mailto:ilyas.ibragimov@outlook.com}{ilyas.ibragimov@outlook.com} \\
\href{https://www.linkedin.com/in/ilyasi/}{linkedin.com/in/ilyasi} \\
\href{https://ilyasi.com}{ilyasi.com}

\vspace{1em}

\noindent Hi,

\vspace{1em}

\noindent I'm a backend engineer at Two Sigma. For the past few years I've built and maintained a firm-wide cost platform, 15+ TB daily across 8+ data sources, tracking \$80MM+ in annual spend. A lot of that work comes down to access and ownership modeling across a large org, which is close to what you're describing.

\vspace{1em}

\noindent Before that I was at Blueshift Asset Management. Built a real-time P\&L and portfolio monitoring system from scratch, a compliance system that flagged bad trades before execution, integrated with equity and crypto exchanges, and optimized their C++ trading platform. It was a small team and I got to touch a lot of different parts of the stack.

\vspace{1em}

\noindent I'm based in NYC and happy to be in office. I work mostly in Python, BigQuery, and SQL. Django and PostgreSQL I know well enough to be useful from day one, just not what I use daily.

\vspace{1em}

\noindent Thank you for your consideration,

\vspace{1em}

\noindent Ilyas \\
\href{mailto:ilyas.ibragimov@outlook.com}{ilyas.ibragimov@outlook.com} $|$ \href{https://www.linkedin.com/in/ilyasi/}{linkedin.com/in/ilyasi} $|$ \href{https://ilyasi.com}{ilyasi.com}

\end{document}
