%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Editor : Ilyas Ibragimov
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% Conditional phone number: compile with \def\includephone{1} to include
\newif\ifincludephone
\ifdefined\includephone \includephonetrue \fi

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{cmap}           % Embed CMap tables for PDF text extraction
\usepackage[T1]{fontenc}    % 8-bit font encoding (proper dashes, accents, ligatures)
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% Custom colors
\definecolor{sectionblue}{RGB}{30, 50, 80}
\definecolor{dividerline}{RGB}{210, 210, 210}

% Hyperlink styling
\hypersetup{
  colorlinks=true,
  urlcolor=sectionblue,
  linkcolor=sectionblue,
  pdftitle={Ilyas Ibragimov - Senior Software Developer},
  pdfauthor={Ilyas Ibragimov},
  pdfsubject={Resume},
  pdfkeywords={Software Engineer, Python, BigQuery, dbt, SQL, C++, LLM, Two Sigma, Data Engineering, GCP}
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\color{sectionblue}
}{}{0em}{}[\color{sectionblue}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize #1} & {\small #2} \\
      {\small\color{sectionblue}\textbf{#3}} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingLarger}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize #1} & {\small #2} \\
      \textit{\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEduHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize #1} & {\small #2} \\
      \hspace{0.15in}\textit{\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{0.15in}\textit{\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\setlength{\itemsep}{0pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape \color{sectionblue} ILYAS IBRAGIMOV} \\ \vspace{-1pt}
    \small New York, NY \textbar{}
    \ifincludephone 929-529-4148 \textbar{} \fi
    \href{mailto:ilyas.ibragimov@outlook.com}{ilyas.ibragimov@outlook.com} \textbar{}
    \href{https://www.linkedin.com/in/ilyasi/}{linkedin.com/in/ilyasi}
    \textbar{}
    \href{https://ilyasi.com}{ilyasi.com}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Software engineer with 6+ years at quantitative hedge funds building platform infrastructure and trading systems. At Two Sigma, lead the backend for firm-wide cost and metrics platforms tracking \$200M+ in annual cloud, GenAI, and engineering spend across hundreds of products. Built multiple LLM-powered tools in production. Previously reported directly to the CTO at a \$500M+ hedge fund, building portfolio monitoring, compliance, and automated reporting systems while optimizing the firm's proprietary C++ trading platform.
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Developer}{Nov. 2022 -- Present}
      {Two Sigma}{New York, NY}
      \resumeItemListStart
        \resumeItem{Stepped up to lead the backend effort on a firm-wide cost transparency platform tracking \$200M+ in annual spend. Developed and maintained the ELT backend over 3 years in Python, dbt, and BigQuery, ingesting 15+ TB daily from 8+ data sources across hundreds of products.}
        \resumeItem{Led the migration from Apptio to Python, dbt, and BigQuery, delivering \$1M+ in annual savings and 65\% faster processing. Drove early adoption of dbt (Data Build Tool) at the firm, co-authoring the internal best practices guide, building quickstart repos, and giving presentations that accelerated usage across multiple teams.}
        \resumeItem{Built a firm-wide metrics platform in Python, BigQuery, and SQL, ingesting hundreds of KPIs from multiple teams and sources for executive dashboards (Backstage) and team-level tracking.}
        \resumeItem{Managed team transitions (offboarded an engineer, onboarded his replacement), then partnered with the new engineer to decompose a legacy monolith into 5 loosely coupled pipelines with CI/CD, automated testing, and schema drift auto-recovery.}
        \resumeItem{Built GenAI-powered systems using Claude and Vertex AI: an automated incident response pipeline with Slack alerting and root-cause analysis, and a department reorganization detector that classifies org changes and applies retroactive cost corrections, eliminating weeks of manual investigation.}
      \resumeItemListEnd
    \vspace{1pt}

    \resumeSubheading
      {Software Developer}{Jan. 2020 -- Nov. 2022}
      {Blueshift Asset Management}{Red Bank, NJ}
      \resumeItemListStart
        \resumeItem{Built a real-time portfolio monitoring platform with terminal-based GUI, automated investor reporting, and historical performance tracking. Reduced analysis time by 65\% and supported \$500M+ in managed assets.}
        \resumeItem{Optimized the fund's proprietary C++ trading platform, reducing storage by tens of terabytes and production server load by 40\%.}
        \resumeItem{Integrated with multiple equity and crypto exchanges and built Python/Selenium data scrapers feeding alternative data research: social media signals, transcribed investor calls, and market sentiment analysis.}
        \resumeItem{Designed a real-time compliance monitoring system automatically flagging banned tickers and improper trade amounts before execution, preventing regulatory violations.}
      \resumeItemListEnd
    \vspace{1pt}

    \resumeSubheading
      {Platform Development Intern}{July 2018 -- Sep. 2018}
      {Fidessa}{Woking, UK}
      \resumeItemListStart
        \resumeItem{Built a secure file transmission platform in Java and JavaScript that eliminated recurring data breaches affecting 200+ clients, replacing vulnerable manual processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEduHeading
      {University College London (UCL)}{London, UK}
      {Master of Engineering, Electronic \& Electrical Engineering}{2018 -- 2019}
    \resumeSubSubheading
      {Bachelor of Engineering, Electronic \& Electrical Engineering}{2015 -- 2018}
    \resumeSubSubheading
      {First Class Honors \textperiodcentered{} 4.0 GPA Equivalent}{}
    \vspace{-5pt}
    \resumeEduHeading
      {Baruch College MFE Program}{New York, NY}
      {C++ Programming for Financial Engineering Certificate, Distinction}{2020}
    \resumeEduHeading
      {Brooklyn Technical High School}{Brooklyn, NY}
      {High School Diploma, Mathematics Major, Math Team, 4.0 GPA}{2011 -- 2015}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL (BigQuery), C++, Bash, JavaScript, HTML/CSS} \\
     \textbf{Data \& Analytics}{: dbt, BigQuery, PostgreSQL, Dimensional Modeling, ELT Pipeline Design} \\
     \textbf{Cloud \& Infrastructure}{: GCP (BigQuery, GCS), AWS, Docker, Argo, GitHub Actions, Linux/Unix} \\
     \textbf{AI/GenAI}{: Claude Code, Claude API, Vertex AI, MCP Servers, AI Pipelines, Agentic Workflows, AI Integration} \\
     \textbf{Tools \& Frameworks}{: Git, GitHub, Datadog, Jira, Slack, Flask, Django, Playwright, Selenium}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubheadingLarger
        {Network Packet Routing with Deep Reinforcement Learning}{MEng Thesis, First Class Honors}
        {University College London (UCL)}{2019}
        \resumeItemListStart
          \resumeItem{Developed deep reinforcement learning models for optimal packet routing in software-defined networks using Python, OpenAI Gym, and TensorFlow.}
        \resumeItemListEnd
      \resumeSubheadingLarger
        {Deep Learning Applications in Cryptocurrency Trading}{BEng Thesis, First Class Honors}
        {University College London (UCL)}{2018}
        \resumeItemListStart
          \resumeItem{Built and refined LSTM networks for cryptocurrency return prediction using Python/Keras with extensive feature engineering and data mining.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
